Amphistomy increases leaf photosynthesis more in coastal than montane plants of Hawaiian ʻilima (\emph{Sida fallax})

### 2023-12-13 ms/ms.tex
added Zenodo link to ms

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

Custom scripts are available on a GitHub repository
(https://github.com/cdmuir/stomata-ilima) and archived on Zenodo (). Raw
data are deposited on Dryad (https://doi.org/10.5061/dryad.rxwdbrvfw ).

>>>>

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, sharp corners, enhanced, breakable, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Custom scripts are available on a GitHub repository
(https://github.com/cdmuir/stomata-ilima) and archived on Zenodo
(https://doi.org/10.5281/zenodo.10369114). Raw data are deposited on
Dryad (https://doi.org/10.5061/dryad.rxwdbrvfw ).
